The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-17 dit-paper_ieee.tex
added knuth reference

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values the problem of
		finding the corresponding DIT is an instance of the Chinese Remainder Problem
		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
		moduli \cite{gauss1965disquisitiones}. (note that $x^{-1} \; (mod \; y)$
		means the modular inverse of $x$ in the naturals modulo $y$)

>>>>

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values the problem of
		finding the corresponding DIT is an instance of the Chinese Remainder Problem
		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
		moduli \cite{gauss1965disquisitiones,knuth1969art}. (note that $x^{-1} \; (mod
		\; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
